### 2023-07-17 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

 Fig.~\ref{fig:fasernu2_muon} displays the
 event yields per bin,  Eq.~(\ref{eq:event_yields}),
 for muon neutrinos detected at the
 FASER$\nu$, SND@LHC, FASER$\nu$2, and FLArE  experiments,
 restricted
 to the DIS region defined by Eq.~(\ref{eq:DISconditions})
 and where only bins with $\ge 30$ events are retained.
 %
 Adding up the bins in each of the panels results into the numbers listed in
 Table~\ref{tab:integrated_rates}.
 %
 The clear improvement in going frm FASER$\nu$, SND@LHC
 to the FPF experiments related not only to the number
 of events but also to the kinematic coverage,
 %
 For the FPF experiments,m 
 One observes large event rates for most of the region in $\lp x,Q^2\rp$ covered,
 leading to typical statistical uncertainties at the 1\% level or smaller,
 while for FASER$\nu$, SND@LHC statistical uncertainties are much larger.

@@

Fig.~\ref{fig:fasernu2_muon} indicates
how the kinematic coverage of FASER$\nu$2 reaches
$x_{\rm min}\sim 3\times 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 2\times 10^3$
at large-$Q^2$, representing an extension
of around one order of magnitude in both directions as compared to available
DIS neutrino data on nuclear targets.
%
Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF} compares
the kinematic coverage of FASER$\nu$2 with that of electron-ion collisions
at the upcoming EIC~\cite{Khalek:2021ulf,AbdulKhalek:2021gbh}
and to other available hard-scattering datasets involving
nuclear targets or projectiles.
%
Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
production in proton-lead collisions at the LHC entering the  nNNPDF3.0
determination~\cite{AbdulKhalek:2022fyi}.

@@

The event yields displayed in Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2, and the corresponding
calculations for the other experiments listed in Table~\ref{tab:FPF_experiments},
determine the associated statistical uncertainty in each bin
\be
\label{eq:statistical_uncertainties}
\delta^{\rm (stat)}  N_{\rm ev}^{(i)} = \sqrt{N_{\rm ev}^{(i)}} \, ,
\ee
such that the fractional statistical uncertainty per bin is $\delta^{\rm (stat)}_i=1/\sqrt{N_{\rm ev}^{(i)}}$.
%
Since we discard bins with less than 30 events, the fractional statistical uncertainty
ranges between $\lsim 1\%$ and $\sim 18\%$ for muon neutrinos in
the case of FASER$\nu$2 depending on the values of
$x$ and $Q^2$ associated to this bin.

@@

These statistical uncertainties are displayed in the left panel
of Fig.~\ref{fig:error_plot_FASERv2_14}, which corresponds
to the same event yields as in
Fig.~\ref{fig:fasernu2_muon}
now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$.
%
The error bar in the vertical direction indicates the statistical uncertainties, while
that in the horizontal direction corresponds to the width of the $x$-bins.
%
Except for the bins with the smallest values of $x$, statistical uncertainties indeed
are at the percent level for FASER$\nu$2.

@@

For each possible source of experimental systematic uncertainty, we therefore need to
quantify its impact at the event yield level.
%
In order to determine these bin-by-bin systematic uncertainties,
we extend the calculation delineated in Eq.~(\ref{sec:pseudo-data_generation}) as follows.
%
Let us consider for illustrative purposes the FASER${\nu}$2 case.
%
From Table~\ref{tab:FPF_experiments}, one reads that the detector
acceptance and reconstruction performance is specified by:
\bea
E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.5)\, , \qquad \nonumber\\
\delta E_\ell \sim 30\% \, 
 \quad \delta E_h \sim 30\% \, ,
 \ \, , \quad \delta\theta_\ell \sim 1~{\rm mrad} \, . 
\label{eq:fasernu2systematic_errors}
\eea
To translate the uncertainties in $\delta E_\ell$, $\delta E_h $,
and $\delta\theta_\ell$ into systematic errors associated to the event yields, 
\be
\label{eq:event_yields_systematic_error}
\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} \, ,\quad
\delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(i)}
\, ,\quad
\delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(i)} \, ,\qquad i=1,\ldots,N_{\rm bin} \, ,
\ee
we generate first a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
composed by $N_{\rm mc} = 10^7$ samples and determine the assignment of each event
to a point in the $\lp x,Q^2,E_{\nu}\rp$ space.
%
By integrating over this sample by means of Eq.~(\ref{MCintegration}) we determine
the binned event yields for this reference $\mathcal{D}_0$ sample.

We then produce a second Monte Carlo sample $\mathcal{D}_1$ starting from the events
of $\mathcal{D}_0$ which are then smeared with Gaussian distributions whose variances
are given by Eq.~(\ref{eq:fasernu2systematic_errors}).
%
The bin assignment of the events in the smeared sample $\mathcal{D}_1$ will
in general be different from those of the baseline sample.
%
The procedure is repeated $M$ times, leading to
$\mathcal{D}_k$ (with $k=1,\ldots,M$) smeared
samples each one leading to a different binned event yields
$ N_{\rm ev}^{(i)(k)}$.
%
We take the uncertainty to be the absolute difference between the mean number of events in the bin for the smeared samples samples, ${\overline{N}}^{(i)}~$ and$~ N_{\rm ev}^{(i)}$ as calculated from Eq. \ref{MCintegration}, {\it{i.e.}}  $\delta N^{(i)} = |{\overline{N}}^{(i)} -N_{\rm ev}^{(i)}|$ .
%
Furthermore, 
since the systematic errors are treated as uncorrelated among them,
by producing samples where only one source of error is varied at a time
we can determine the systematic errors Eq.~(\ref{eq:event_yields_systematic_error}) in each bin.

>>>>

 Fig.~\ref{fig:fasernu2_muon} displays the
 event yields per bin,  Eq.~(\ref{eq:event_yields}),
 for muon neutrinos detected at the
 FASER$\nu$, SND@LHC, FASER$\nu$2, and FLArE  experiments,
 restricted
 to the DIS region defined by Eq.~(\ref{eq:DISconditions})
 and where only bins with $\ge 30$ events are retained.
 %
 Adding up the bins in each of the panels results into the numbers listed in
 Table~\ref{tab:integrated_rates}.
 %
 The clear improvement in going from the current FASER$\nu$ and SND@LHC
 experiments to the FPF ones is visible both in terms
 of the number
 of events per bin as well as for the kinematic coverage.
 %
 The FPF experiments benefit from large
 event rates for most of the region in $\lp x,Q^2\rp$ covered,
 leading to typical statistical uncertainties at the 1\% level or smaller,
 while for FASER$\nu$, SND@LHC statistical uncertainties are much larger due
 to the reduced event rates.

@@

Fig.~\ref{fig:fasernu2_muon} indicates
how the kinematic coverage of the FPF far-forward experiments reaches
$x_{\rm min}\sim \times 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 2\times 10^3$
at large-$Q^2$, representing an extension
of around one order of magnitude in both directions as compared to available
DIS neutrino data on nuclear targets.
%
Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF} compares
the kinematic coverage of FASER$\nu$2, FLArE, and AdvSND with that of electron-ion collisions
at the upcoming EIC~\cite{Khalek:2021ulf,AbdulKhalek:2021gbh}
and to other available hard-scattering datasets involving
nuclear targets or projectiles.
%
Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
production in proton-lead collisions at the LHC entering the  nNNPDF3.0
determination~\cite{AbdulKhalek:2022fyi}.
%
The LHC neutrino experiments cover the region $x\gsim 10^{-3}$ relevant
for precision electroweak measurements at the LHC, such as the $W$-boson
mass, and for new physics measurements sensitive to the large-$x$ quarks
and antiquarks in the proton.

@@

The event yields displayed in Fig.~\ref{fig:fasernu2_muon} 
determine the associated statistical uncertainty in each bin by means of
\be
\label{eq:statistical_uncertainties}
\delta^{\rm (stat)}  N_{\rm ev}^{(i)} = \sqrt{N_{\rm ev}^{(i)}} \, ,
\ee
such that the fractional statistical uncertainty per bin is $\delta^{\rm (stat)}_i=1/\sqrt{N_{\rm ev}^{(i)}}$.
%
Since we discard bins with less than 30 events, the fractional statistical uncertainty
ranges between $\lsim 1\%$ and $\sim 18\%$, depending on the values of
$x$ and $Q^2$ associated to this bin.

@@

These statistical uncertainties are displayed in the left panel
of Fig.~\ref{fig:error_plot_FASERv2_14}, which corresponds
to the same event yields as in
Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2
now as a function of $x$ after having integrated the event
yields in the range $Q^2 \in [10,100]$ GeV$^2$.
%
The error bar in the vertical direction indicates the statistical uncertainties, while
that in the horizontal direction corresponds to the width of the $x$-bins.
%
Except for the bins with the smallest values of $x$, statistical uncertainties indeed
are at the percent level or smaller for FASER$\nu$2.

@@

For each source of experimental systematic uncertainty we need to
quantify its impact at the event yield level.
%
In order to determine these bin-by-bin systematic errors,
we extend the calculation delineated in Eq.~(\ref{sec:pseudo-data_generation}) as follows.
%
Let us consider for illustrative purposes the FASER${\nu}$2 detector.
%
From Table~\ref{tab:FPF_experiments} we know that its
acceptance and reconstruction performance are specified by:
\bea
E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.025)\, , \qquad\\
\delta E_\ell \sim 30\% \, 
 \quad \delta E_h \sim 30\% \, ,
 \quad \delta\theta_\ell \sim 0.06~{\rm mrad} \, . 
\label{eq:fasernu2systematic_errors}
\eea
To translate the uncertainties in $\delta E_\ell$, $\delta E_h $,
and $\delta\theta_\ell$ into systematic errors associated to the event yields, 
\be
\label{eq:event_yields_systematic_error}
\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} \, ,\quad
\delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(i)}
\, ,\quad
\delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(i)} \, ,\qquad i=1,\ldots,N_{\rm bin} \, ,
\ee
we generate first a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
composed by $N_{\rm mc} = 10^7$ samples and determine the assignment of each event
to a point in the $\lp x,Q^2,E_{\nu}\rp$ space.
%
By integrating over this sample by means of Eq.~(\ref{MCintegration}), we determine
the binned event yields for this reference $\mathcal{D}_0$ sample.

We then produce a second Monte Carlo sample $\mathcal{D}_1$ starting from the events
of $\mathcal{D}_0$ which are then smeared with Gaussian distributions whose variances
are given by Eq.~(\ref{eq:fasernu2systematic_errors}).
%
The bin assignment of the events in the smeared sample $\mathcal{D}_1$ will
in general be different from those of the baseline sample.
%
The procedure is repeated $M$ times, leading to
$\mathcal{D}_k$ (with $k=1,\ldots,M$) smeared
samples each one leading to a different binned event yields
$ N_{\rm ev}^{(i)(k)}$.
%
We take the uncertainty associated
to a given systematic source, say $\delta E_\ell$,
to be the absolute difference between the mean number of events in this
bin evaluated for the smeared samples samples and the
central prediction for the number of events
$ N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{MCintegration}):
\be
\delta_{\rm sys}^{(E_\ell)} N^{(i)} = \Big| \la {N}^{(i)}\ra_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big| \, .
\ee
Systematic errors are treated as uncorrelated among them and hence
by producing samples where only one source of error is varied at a time
we can determine the systematic errors, Eq.~(\ref{eq:event_yields_systematic_error}), in each bin.
%
This approach has the benefit that rescaling individual sources of systematic
uncertainties, say to assess the impact of improved detector performance,
are straightforward.
